Setting up Data

### 2020-05-12 src/SetupData.Rmd
updating the setupscript, move DMC1 DF setup

#opts_knit$set(root.dir = "~./MLH1repo/")
#setwd("~./MLH1repo/")

meta.data = read.csv(here("data", "/clean.Meta.Data.txt"), sep = "\t", header=TRUE)
#remove all MAD (peromyscus) from meta.data
#meta.data <- meta.data[ !grepl("MAD", meta.data$mouse) , ]

source(here("src", "/CommonFunc_MLH1repo.R") )

#MLH1_data = read.csv(here("data", "/AnonData.csv"), sep="\t", header=TRUE)
#read.csv was breaking things
MLH1_data = read.xlsx2(here("data", "/AnonData_formated.xlsx"), header=TRUE, 1)

#formating the original anon file
#MLH1_data = read.xlsx2(here("data", "/AnonData.xlsx"), header=TRUE, 1)
#MLH1_data$fileName <- (MLH1_data$Original.Name)

#MLH1_data <- add_mouse(MLH1_data)
#MLH1_data <- add_category(MLH1_data)
#MLH1_data <- add_strain(MLH1_data)
#MLH1_data <- add_sex(MLH1_data)
#MLH1_data <- add_subsp(MLH1_data)
#MLH1_data <- add_species(MLH1_data)
#write csv to MLH1 file
#write.xlsx2(MLH1_data, "AnonData_formated.xlsx", sheetName="Sheet1",
#  col.names=TRUE, row.names=FALSE, append=FALSE)
```

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.5.20.RData")

>>>>

opts_knit$set(root.dir = "~./MLH1repo/")
setwd("~./MLH1repo/")

meta.data = read.csv( "~./MLH1repo/data/clean.Meta.Data.txt", sep = "\t", header=TRUE)
#remove all MAD (peromyscus) from meta.data
#meta.data <- meta.data[ !grepl("MAD", meta.data$mouse) , ]

source("~./MLH1repo/src/CommonFunc_MLH1repo.R" )

#MLH1_data = read.csv(here("data", "/AnonData.csv"), sep="\t", header=TRUE)
#read.csv was breaking things
MLH1_data = read.xlsx2("~./MLH1repo/data/AnonData_formated.xlsx", header=TRUE, 1)

DMC1.DF <- read.csv("~./MLH1repo/data/DMC1newJuviQuant.csv", header = TRUE)

@@

#DMC1 Sections

move the chunk below to setup

```{r DMC1.setup, echo=FALSE}
#load DMC1 csv
#DMC1.DF <- read.csv("~./DMC1/newJuviQuant.csv", header = TRUE)

DMC1.DF$fileName <- DMC1.DF$Original.Name
DMC1.DF <- add_mouse(DMC1.DF)
DMC1.DF <- add_strain(DMC1.DF)
DMC1.DF <- add_category(DMC1.DF)
DMC1.DF <- add_subsp(DMC1.DF)
DMC1.DF <- DMC1.DF[DMC1.DF$stage != "P",]

#make DMC1 table
DMC1.mean.obs.L <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Early",],
                 .(category),
                 summarize,

                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.L$stage <- "early Z"

DMC1.mean.obs.Z <- ddply(.data=DMC1.DF[DMC1.DF$stage == "Late",],
                 .(category),
                 summarize, 
                 ncells = length(fileName),
                 mean.count = mean( total.count)
)
DMC1.mean.obs.Z$stage <- "late Z"

DMC1.mean.table <- rbind(DMC1.mean.obs.L,DMC1.mean.obs.Z)

DMC1.DF$rec_group <- ifelse(grepl("WSB", DMC1.DF$strain), "Low",
                          ifelse(grepl("G",DMC1.DF$strain), "Low",

              ifelse(grepl("KAZ", DMC1.DF$strain), "Low",
            ifelse(grepl("PWD", DMC1.DF$strain), "High",
               ifelse(grepl("MSM", DMC1.DF$strain), "High","")))))
```

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.12.20.RData")
